Tutorials: A Brief Overview

### 2023-04-26 tutorials.qmd
update to documentation buttons

---
title: "Tutorials: A Brief Overview"
number-sections: true
format:
 html:
   css: styles.css
   theme: cosmo
   fontsize: 1.1em
   linestretch: 1.5
---

## What are Tutorials?

::: {style="text-align: justify; font-size: 1.2em; line-stretch: 1.o; font-family: Georgia, serif;"}
[**The primary goal**]{style="color: goldenrod; font-size: 1.2em; font-family: Verdana, sans-serif;"} 
of the tutorial section is to help users learn and understand a specific topic or method by providing an introductory and hands-on, step-by-step guide. This section aims to create engaging, accessible, and effective entry learning experiences that enable users to develop their skills and understanding of the subject matter. 
:::

>>>>

---
title: "Tutorials: A Brief Overview"
number-sections: false
format:
 html:
   css: styles.css
   theme: cosmo
   fontsize: 1.1em
---

## <i class="bi bi-book"></i> What are Tutorials?

::: {style="text-align: justify; font-size: 1.2em; line-stretch: 1.0; font-family: Georgia, serif;"}
[**The primary goal**]{style="color: goldenrod; font-size: 1.2em; font-family: Verdana, sans-serif;"} 
of the tutorial section is to help users learn and understand a specific topic or method by providing an introductory and hands-on, step-by-step guide. This section aims to create engaging, accessible, and effective entry learning experiences that enable users to develop their skills and understanding of the subject matter. 
:::
